---
page-layout: full
title: "Teaching"
echo: false
warning: false
---
```{r}
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(knitr))
suppressPackageStartupMessages(library(kableExtra))
suppressPackageStartupMessages(library(readxl))
```

## Machine Learning Basics Workshop Series

This workshop is held in Winter 2023 for the members of Transportation Systems Innovation Lab at University of Windsor.

## Data Analytics Instructor at St. Clair College

```{r}
tribble(
  ~Semester, ~ `Course(s)`,
  "Winter 2023", "Capstone Project",
  "Fall 2022", "Machine Learning I",
  "Spring 2022", "Capstone Project", 
  "Winter 2022", "Machine Learning I,\nCapstone Project",
  "Fall 2021", "Intro. to Artificial Intelligence,    Machine Learning I",
  "Spring 2021", "Machine Learning I,    Basic Statistics and Exploratory Data Analysis",
  "Winter 2021", "Analytic Tools and Decision Making,    Basic Statistics and Exploratory Data Analysis",
  "Fall 2020", "Analytic Tools and Decision Making,   Ethics for Analytics",
  "Spring 2020", "IT Service Management",
  "Fall 2019", "Analytic Tools and Decision Making",
  "Spring 2019", "IT Service Management"
) %>% 
  # mutate_all(linebreak) %>% 
  knitr::kable(
    format = "html",
    align = "l",
    booktabs = TRUE,
    longtable = TRUE,
    linesep = c("\\addlinespace")
    ) %>%
  kable_styling()
```

- [Capstone Projects (Spring 2022)](https://dab402003.netlify.app/)  



## Graduate Assistant at University of Windsor

```{r}
read_excel("ga_experience.xlsx") %>% 
 relocate(Semester) %>% 
 knitr::kable(
    format = "html",
    align = "l",
    booktabs = TRUE,
    longtable = TRUE,
    linesep = c("\\addlinespace")
    ) %>%
  kable_styling()
```

- [Interactive Course: R for Driving Simulator Data](https://umair.shinyapps.io/R_for_driving_sim/)  


## Lecturer/Lab Engineer at University of Engineering & Technology, Lahore (2010 - 2012)

Subjects taught:  

- Railway Engineering  
- Construction Management  
- Construction Materials and Machinery  





## Guest Lectures  

- ["Reaction Time in Car-following"](https://www.youtube.com/watch?v=-wwKrQG1KyY) Lecture for *Institute of Highway Engineers*, UK. 
 


