---
page-layout: full
title: "Talks and Teaching"
echo: false
warning: false
---
```{r}
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(knitr))
suppressPackageStartupMessages(library(kableExtra))
suppressPackageStartupMessages(library(readxl))
```

## A Mini Tour of Open-source tools for Transportation Planning & Engineering

In November 2023, I gave a talk to University of Windsor chapter of Institute of Transportation Engineers (ITE). The slides are embedded below:  

```{=html}
<iframe width="780" height="500" src="https://dru.quarto.pub/slides/#/section"></iframe>
```


## Scaling Shiny Apps with Google’s Firebase

I gave a talk in October 2023 at Windsor Devfest 2023, organized by Google Developers Group Windsor, Ontario. The talk was titled `Catching Fire: Scaling Shiny Apps with Google’s Firebase`.  

```{=html}
<iframe width="780" height="500" src="https://durraniu.github.io/gdg_talk/#/title-slide"></iframe>
```

* GitHub: https://github.com/durraniu/gdg    
* App: https://umair.shinyapps.io/GoogleDevelopersGroupShiny/_w_f3eb35a9/ 

## Machine Learning Basics Workshop Series

This workshop was held in Winter 2023 for the members of Transportation Systems Innovation Lab at University of Windsor.

## Data Analytics Instructor at St. Clair College

```{r}
tribble(
  ~Semester, ~ `Course(s)`,
  "Winter 2023", "Capstone Project",
  "Fall 2022", "Machine Learning I",
  "Spring 2022", "Capstone Project", 
  "Winter 2022", "Machine Learning I,\nCapstone Project",
  "Fall 2021", "Intro. to Artificial Intelligence,    Machine Learning I",
  "Spring 2021", "Machine Learning I,    Basic Statistics and Exploratory Data Analysis",
  "Winter 2021", "Analytic Tools and Decision Making,    Basic Statistics and Exploratory Data Analysis",
  "Fall 2020", "Analytic Tools and Decision Making,   Ethics for Analytics",
  "Spring 2020", "IT Service Management",
  "Fall 2019", "Analytic Tools and Decision Making",
  "Spring 2019", "IT Service Management"
) %>% 
  # mutate_all(linebreak) %>% 
  knitr::kable(
    format = "html",
    align = "l",
    booktabs = TRUE,
    longtable = TRUE,
    linesep = c("\\addlinespace")
    ) %>%
  kable_styling()
```

- [Capstone Projects (Spring 2022)](https://dab402003.netlify.app/)  



## Graduate Assistant at University of Windsor

```{r}
read_excel("ga_experience.xlsx") %>% 
 relocate(Semester) %>% 
 knitr::kable(
    format = "html",
    align = "l",
    booktabs = TRUE,
    longtable = TRUE,
    linesep = c("\\addlinespace")
    ) %>%
  kable_styling()
```

- [Interactive Course: R for Driving Simulator Data](https://umair.shinyapps.io/R_for_driving_sim/)  


## Lecturer/Lab Engineer at University of Engineering & Technology, Lahore (2010 - 2012)

Subjects taught:  

- Railway Engineering  
- Construction Management  
- Construction Materials and Machinery  





## Guest Lectures  

- ["Reaction Time in Car-following"](https://www.youtube.com/watch?v=-wwKrQG1KyY) Lecture for *Institute of Highway Engineers*, UK. 
 


